
---
title: "Esophageal Cancer"
subtitle: "Surgery"
author: "Jonathan Salo MD"
institute: "Levine Cancer Institute, Charlotte NC"
#date: "Click Down Arrow to Begin"
#date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
  html_document: default
  pdf_document: default
---
<style type="text/css">
.remark-slide-content {
    font-size: 34px;
    padding: 1em 4em 1em 4em;
}
</style>
<!--- P10000266--->
<!--- Premiere: Intro_02--->
# Introduction

I’m Dr Jonathan Salo,  a GI Cancer Surgeon in Charlotte, North Carolina.

In this video, you will learn about

- Different kinds of surgery for esophageal cancer
- Choosing a surgical team

---

Surgery for esophageal cancer is generally performed for three different situations:

- Superficial Tumors (T1) that can't be completely removed by endoscopy
- Localized Tumors (T2N0)
- Locally Advanced Tumors (T3 or N+) after the completion of chemotherapy and radiation

---

# Goals of Esophagectomy

- Remove tumor from esophagus
- Remove surrounding lymph nodes
- Reconstruct gastrointestinal tract

---

# Types of Esophagectomy

Many different types of esophagectomy and several different techniques.

Esophagus connects the throat to the stomach

Total esophagectomy removes all of the esophagus and makes a new connection in the neck. This new connection is called an anastomosis.

Subtotal esophagectomy removed 75% of the esophagus and makes a new connection in the chest.

---

# Total Esophagectomy

There are two types of total esophagectomy:

**McKeown** esophagectomy makes incisions in the abdomen, the right chest, and the neck

**Transhiatal** esophagectomy uses an incision in the abdomen and the neck, and creates a tunnel in the chest cavity.

---

# Subtotal Esophagectomy

The subtotal esophagectomy makes incisions in the abdomen and the right chest. This is also known as the *Ivor Lewis* esophagectomy.

---

# Esophagectomy Techniques

For each of the different approaches, there are different surgical techniques:

- Open technique uses a laparotomy and thoracotomy incisions.

- Minimally-invasive technique uses small incisions and specialized instruments

The minimally-invasive approach offers less discomfort and faster healing. An open approach is occasionally required for larger tumors.

# Esophageal Reconstruction

After the esophagus has been removed, it is necessary to construct a new esophagus.  In the vast majority of cases, a new esophagus is fashioned from the stomach. The stomach is then brought up into the chest to replace the esophagus.  A new connection is made between the esophagus and the stomach called the **anastomosis**.

---

The decisions regarding the right operation for a particular patient is made by the surgeon and the patient together. The factors involved in making the decision are:

- Location and size of the tumor
- Patient's overall health
- Surgeon's experience and preferences

---



# Risks of Surgery

An esophagectomy is a substantial operation, and it is associated with multiple risks. These can be categorized as follows:

- Irregular heart rhythm (atrial fibrillation)
- Pneumonia
- Anastomotic leak
- Death

---

# Arrhythmia

The esophagus normally lives right next to the heart, and as a result, it is common for the heart to be irritated during the course of esophagectomy.  In some cases, the heart rhythm can become irregular and the heart beats faster than normal.  If this happens, medicines can be required to slow the heart and restore a normal rhythm. 

---

# Pneumonia

Pneumonia is another common complication after esophagectomy, due in part to fact that esophagus is close to the right lung. 

---

# Anastomotic Leak

In most cases, the new connection between the esophagus and stomach, called the anastomosis, heals well.  If connection does not heal properly, this can cause a leakage of fluid from inside the esophagus.  This is called an anastomotic leak.  In some cases, the leak will heal on its own, but other cases may require additional procedures or even surgery.

---

# Death

An esophagectomy is a substantial operation.  It is unusual, but in some cases complications after surgery can result in death.  The risk of death depends upon the overall health of the patient, the tumor, and other factors.

---

# Risks of Complications

The risk of complications depends on three things:

- Hospital Volume
- Surgeon Experience
- Patient's overall health

---

# Understanding Outcomes

Let's talk Baseball for a minute.  Micky Mantle is regarded as one of baseball's greats, and this baseball card from 1952 is one of the most valuable in history.

If you look at the back of his card, you'll find lost of statistics, including his batting average. The numbers are there for anyone to see, including his batting average. If you're a baseball fan, one of the ways you evaluate players is based upon their statistics.

Unfortunately, there aren't baseball cards for hospitals and surgeons, and finding the statistics for a hospital or surgeon can be a challenge, but it's still important if you want the best chance for a good outcome after surgery.

---

# Hospital Volume

<small>Practice makes perfect in many things in life, and esophageal surgery is no exception.</small>

Hospitals where an esophagectomy is performed more frequently in general have better outcomes than hospitals where the operation is only occasionally done. 

---

This chart shows the relationship between hospital volume and the risk of death after esophagectomy.


```{r, echo=F,  fig.height=6,fig.width=8}
library(ggplot2)
df<-data.frame(mortality=c(.102,.067,.039),strength=c("Low (<5)","Middle (5-20)","High (>20)"),mortality_labels =c("10.2%\nLow\nVolume","6.7%\nMiddle","3.9%\nHigh"))
strengths=c("Low (<5)","Middle (5-20)","High (>20)")
p<-ggplot(data=df, aes(x=strength,y=mortality))+
  geom_bar(stat="identity", fill="steelblue")+scale_x_discrete(limits=strengths)+scale_y_continuous(labels = scales::percent_format(accuracy=1)) +
        geom_text(aes(label=mortality_labels),vjust=1.4, color="white",size=13.5)+
  theme_minimal()+
  theme( axis.text=element_text(size=12,face="bold"),axis.title=element_text(size=14, face="bold"),plot.title = element_text(hjust=0.5,face="bold",size=16)) +
  ggtitle("Hospital Mortality after Esophagectomy") +
  labs(y="Percent Mortality",x="Hospital Operations per year")
p

```
---

<small>The risk of death after esophagectomy is about twice as high in hospitals which perform less than 5 esophagectomy operations per year.</small>


```{r, echo=F, fig.height=6, fig.width=8, include=T}
library(ggplot2)
df<-data.frame(mortality=c(.102,.067,.039),strength=c("Low (<5)","Middle (5-20)","High (>20)"))
strengths=c("Low (<5)","Middle (5-20)","High (>20)")
p<-ggplot(data=df, aes(x=strength,y=mortality))+
  geom_bar(stat="identity", fill="steelblue")+scale_x_discrete(limits=strengths)+scale_y_continuous(labels = scales::percent_format(accuracy=1)) +theme_minimal() + theme( axis.text=element_text(size=12,face="bold"),axis.title=element_text(size=14, face="bold"),plot.title = element_text(hjust=0.5,face="bold",size=16)) +
  ggtitle("Hospital Mortality after Esophagectomy") +
  labs(y="Percent Mortality",x="Hospital Operations per year")
p
ggsave("hosp_mort.png",device="png",path="images/")
```
---

# Finding a Hospital

The easiest way to find out whether a particular hospital is high volume or low volume is to ask your surgeon. 

Another method is to do some research on the internet. The Leapfrog Group is a non-profit organization that collects and published safety in healthcare. Their website ranks hospitals for safety and can help you find a high-volume hospital.  A link to their website is available here: [HospitalSafetyGrade.org](https://www.hospitalsafetygrade.org)

---

# Leapfrog Group Website

You can search on a hospital. Once there, click "View this hospital's leapfrog Hospital Survey Results"

Of course there are low-volume hospital that have good outcomes, but starting with a high-volume hospital is a place to start.

---

The Leapfrog Group 

# Choosing a Surgeon

The surgeon is another key factor in the outcome of an operation.  The Leapfrog recommends a minimum of seven operations per year for surgeons undertaking esophagectomy.

The surgeon's track record of outcomes is also an extremely helpful way to predict outcomes.  Finding out this information may require some uncomfortable questions, but this is important information.  It is critical to know both what the track record of the hospital is, but also the track record of a particular surgeon.

---

# Your Surgeon's Outcomes

Knowing your surgeon's outcomes is important, but knowing your surgeon's outcomes is probably more important.  Your surgeon should be able to tell you what their statistics are for outcomes like anastomotic leak, pneumonia, and death after surgery.

If you surgeon doesn't know their personal statistics, you may want to look for a second opinion.  After all, if you met a professional baseball player, you would expect that they would be familiar with their batting average. 

---

# Questions for Your Surgeon

1) How many esophagectomy operations are performed each year in your hospital?
2) How many esophagectomy operations do you perform personally each year?
3) What are your overall rates of complications?
  - Pneumonia
  - Anastomotic Leak
  - Death in the first 90 days after surgery
  
---











